Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-21 paper/uist_2016/paper.tex
minor edits

Our user study explored the following five metrics as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Location memorability and trip memorability are affected differently by frequency of visits (Figure~\ref{fig:frequencymemory}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.

>>>>

Our user study explored the following five factors as potentially having an effect on memorability, believability, or desirability of digital memory media:
\begin{enumerate}
	\item Distance: how does the location's distance away from the participant's home influence the participant's perception of Rewinds and static photos? Distances ranged from 0 to 206,155 meters. For analysis, these distances were logarithmically scaled and normalized into six distance groups to mimic human categorization of distances into generalizations like ``close,'' ``far,'' or ``very far.'' When normalized: Group 0 corresponded to a range of 0--10 meters from the participant's home location; Group 1 was 10--100 meters; Group 2 was 100--1,000 meters; Group 3 was 1,000--10,000 meters; Group 4 was 10,000--100,000 meters and Group 5 was 100,000--1,000,000 meters from the participant's home location.  
	\item Visit frequency: do participants react differently to Rewinds and static photos depicting locations they visit frequently compared to locations they rarely visit? We showed locations that were either ``most frequently visited,'' ``least frequently visited,'' or randomly selected.
	\item Companions: how does the presence of a traveling companion affect the participant's attitude toward Rewinds or static photos?
	\item Traveler type: do attitudes toward Rewinds and static photos differ depending on whether the participant identifies as a frequent traveler?
	\item GPS usage: do participants who are regular users of GPS navigation react differently to Rewinds and static photos compared to participants who don't use GPS navigation regularly?
\end{enumerate}

@@

\label{table:betweensubjects}

@@

\subsubsection{Visit Frequency}
% only affect location rememberance
% trip rememberance $\chi^2(1,126) = 0.066$, p = 0.3987 (> 0.05)
% most frequently visited - 72%, least frequently visited - 36%, $\chi^2(1,128) = 14.458$, p < 0.01
Location memorability and trip memorability are affected differently by frequency of visits (Table~\ref{table:betweensubjects}). Location memorability is highest for places that are most frequently visited by the participant, while trip memorability is highest for places that are least frequently visited. The more frequently a place was visited, the more likely it was that the participant remembered the location when it was shown to them at the study. In the most frequently visited places, participants remembered the location 72\% of the time, while only remembering the location 36\% of the time in least frequently visited places, with a significance at $\chi^2(1,128) = 14.458$, p < 0.01. This effect does not occur for trip memorability. In the most frequently visited places, trips are remembered 51\% of the time. Instead of seeing trip memorability decrease for least frequently visited places, this factor increases to 56\%.
